DATA 624 Homework 8

### 2020-04-09 DATA624/HW8.Rmd
More work on HW8

where the $x$ values are randome variables uniformly distributed between $[0,1]$ (there are also 5 other non-informative variables also created in the simulation).  The package `mlbench` contains a function called `mlbench.friedman1` that simulates these data:

@@

```{r}
library(caret)
knnModel <- train(x = trainingData$x, 
                  y = trainingData$y,
                  method = "knn",
                  preProcess = c("center", "scale"),
                  tuneLength = 10)
knnModel
```

@@

@@

@@

results %>%
  select(Model, RMSE, Rsquared, MAE) %>%
  arrange(RMSE) %>%
  kable() %>%
  kable_styling()
```
## Question 7.5

>>>>

where the $x$ values are random variables uniformly distributed between $[0,1]$ (there are also 5 other non-informative variables also created in the simulation).  The package `mlbench` contains a function called `mlbench.friedman1` that simulates these data:

@@

### KNN Model

```{r knn_model}
library(caret)
knnModel <- train(x = trainingData$x, 
                  y = trainingData$y,
                  method = "knn",
                  preProcess = c("center", "scale"),
                  tuneLength = 10)
knnModel
```

@@

**The optimal SVM mdoel has a $\sigma$ of `r SVM_model$bestTune$sigma` and an C of `r SVM_model$bestTune$C`.**

@@

```{r}
varImp(SVM_model)
```

**The SVM picked up the important varaibles.**

### Neural Network Model

```{r}
nnet_grid <- expand.grid(.decay = c(0, 0.01, .1), .size = c(1:10), .bag = FALSE)
nnet_maxnwts <- 5 * (ncol(trainingData$x) + 1) + 5 + 1
nnet_model <- train(x = trainingData$x,
                    y = trainingData$y,
                    method = "avNNet",
                    preProcess = c("center", "scale"),
                    tuneGrid = nnet_grid,
                    trControl = trainControl(method = "cv"),
                    linout = TRUE,
                    trace = FALSE,
                    MaxNWts = nnet_maxnwts,
                    maxit = 500)
nnet_model
```

**The best neural network has a size = `r nnet_model$bestTune$size` and a decay of `r nnet_model$bestTune$decay`.**

```{r}
nnet_predictions <- predict(nnet_model, newdata = testData$x)
postResample(pred = nnet_predictions, obs = testData$y)
```

```{r}
varImp(nnet_model)
```

**The top 5 variables are the ones we want to see listed.**

@@

results <- data.frame(t(postResample(pred = nnet_predictions, obs = testData$y))) %>%
  mutate("Model"= "Neural Network") %>%
  bind_rows(results)

results %>%
  select(Model, RMSE, Rsquared, MAE) %>%
  arrange(RMSE) %>%
  kable() %>%
  kable_styling()
```

**The MARS model preformed the best and identified the right variables as the important ones.  The $R^2$ on it is extremely high.  I'm impressed by it's performance on the test set!**

## Question 7.5
